A Machine Learning Approach to MLB Catcher Framing

### 2021-12-09 Slides.Rmd
Added logistic regression

- We used:
- Pitch type and pitch release speed, position, and spin rate
- Whether or not the pitcher and batter are right or left handed
- Count, number of outs during the at-bat, and inning number
- Where the pitch landed
- Whether the game was played home or away

@@

## Slide with Plot

```{r pressure}
plot(pressure)
```

>>>>

- We used:
- Pitch type and pitch release speed, position, and spin rate
- Whether or not the pitcher and batter are right or left handed
- Count, number of outs during the at-bat, and inning number
- Where the pitch landed
- Whether the game was played home or away
- How tall the batter is

@@

## Logistic Regression Model

\tiny
```{r, echo=FALSE}
data_no_catchers <- usable_data[, -18]

train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
test <- (-train)

log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
summary(log_reg_fit)

pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
pred[pred >= 0.5] <- 'strike'
pred[pred < 0.5] <- 'ball'
sum(pred=='strike')/length(pred)

```

```{r}
conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
error <- (conf_mx[2] + conf_mx[3])/length(pred)

conf_mx
error
```
